---
title: "Homework 1"
author: "Bowen Yao"
output: github_document
---

```{r}
library(ggplot2)
```

Problem 1
```{r}
data("penguins", package = "palmerpenguins")
```

The dataset contains measurements of 344 penguins of `r levels(penguins$species)` species;
Variables include species, island, bill length, bill depth, flipper length, 
body mass, sex, and year. Mean bill length is `r round(mean(penguins$bill_length_mm, na.rm = TRUE), 2)`mm, mean bill depth is `r round(mean(penguins$bill_depth_mm, na.rm = TRUE), 2)`mm, 
with mean body mass of `r round(mean(penguins$body_mass_g, na.rm = TRUE), 2)`g.
The dataset has `r nrow(penguins)` rows and
`r ncol(penguins)` columns. The mean flipper length is
`r round(mean(penguins$flipper_length_mm, na.rm = TRUE), 2)` mm.

```{r}
penguin_plot = ggplot(
  penguins,
  aes(
    x = bill_length_mm,
    y = flipper_length_mm,
    color = species
  )
) +
  geom_point(na.rm = TRUE) +
  labs(
    x = "Bill length (mm)",
    y = "Flipper length (mm)",
    color = "Species"
  )

penguin_plot
```


```{r}
ggsave(
  filename = "penguin_scatterplot.png",
  plot = penguin_plot)
```

Problem 2
