---
title: "Homework 1"
author: "Bowen Yao"
output: github_document
---

```{r}
library(ggplot2)
library(tidyverse)
```

##Problem 1
```{r}
data("penguins", package = "palmerpenguins")
```

The dataset contains measurements of 344 penguins of `r levels(penguins$species)` species;
Variables include species, island, bill length, bill depth, flipper length, 
body mass, sex, and year. Mean bill length is `r round(mean(penguins$bill_length_mm, na.rm = TRUE), 2)`mm, mean bill depth is `r round(mean(penguins$bill_depth_mm, na.rm = TRUE), 2)`mm, 
with mean body mass of `r round(mean(penguins$body_mass_g, na.rm = TRUE), 2)`g.
The dataset has `r nrow(penguins)` rows and
`r ncol(penguins)` columns. The mean flipper length is
`r round(mean(penguins$flipper_length_mm, na.rm = TRUE), 2)` mm.

```{r}
penguin_plot = ggplot(
  penguins,
  aes(
    x = bill_length_mm,
    y = flipper_length_mm,
    color = species
  )
) +
  geom_point(na.rm = TRUE) +
  labs(
    x = "Bill length (mm)",
    y = "Flipper length (mm)",
    color = "Species"
  )

penguin_plot
```


```{r}
ggsave(
  filename = "penguin_scatterplot.png",
  plot = penguin_plot)
```

##Problem 2
```{r}
example_df = tibble(
  normal_sample = rnorm(10),
  is_positive = normal_sample > 0,
  character_values = c("a", "b", "c", "d", "e", "f", "g", "h", "i", "j"),
  factor_values = factor(c(
    "low", "medium", "high", "low", "medium",
    "high", "low", "medium", "high", "low"
  ))
)
```

```{r}
mean(pull(example_df, normal_sample))
mean(pull(example_df, is_positive))
mean(pull(example_df, character_values))
mean(pull(example_df, factor_values))
```
The mean works for numeric values, the mean works for logical values because it treated TRUE and FALSE as 1 and 0 so 0.4 is the proportion of values greater than o, the mean dooes not work for charactor and factor because mean() does not accept these types.

```{r, results='hide', warning=FALSE}
as.numeric(pull(example_df, is_positive))
as.numeric(pull(example_df, character_values))
as.numeric(pull(example_df, factor_values))
```
Logical value onverts TRUE to 1 and FALSE to 0, explaining why its mean works.
Character value become NA because they do not represent numbers.
Factor value converts to their integer codes. These codes represent category labels, so meaningless if taken average of.
